\begin{thebibliography}{100}

% ************************* general reviews **********************
\bibitem{VCOX_SLP4CommServ} R. V. Cox, et. al., ``Speech and
language processing for next-millennium communications services'',
Proceedings of the IEEE, Vol. 88, No. 8, Aug. 2000
\bibitem{Juang91Review} B. H. Juang, ``Speech recognition in adverse
environments'', Computer Speech and Language, pp. 275-294, Vol. 5,
1991
\bibitem{Gong95Review} Y. Gong, ``Speech recognition in noisy
environments: A survey'', Speech communication, pp. 261-291, Vol.
16, 1995
\bibitem{Lee98Review} C. H. Lee, ``On stochastic feature and model
compensation approaches to robust speech recognition'', Speech
communication, pp. 29-47, Vol. 25, 1998
\bibitem{Lee00Review} C. H. Lee and Q. Huo, ``On adaptive decision
rules and decision parameter adaptation for automatic speech
recognition'', Proceedings of the IEEE, pp. 1241-1269, Vol. 88, No.
8, Aug. 2000
% Enhancement review
\bibitem{YEphraim04} Y. Ephraim and Isarel Cohen, ``Recent
Advancements in Speech Enhancement'', The Electrical Engineering
Handbook, CRC Press, to appear

\bibitem{ViaVoice} IBM ViaVoice application

\bibitem{AURORA} D. Pearce, H.-G. Hirsch, ``The AURORA experimental framework for the
performance evaluation of speech recogntion systems under noisy
conditions'', \textit{ICSLP, Beijing, China 2000}

\bibitem{HTK} S. Young, et. al., ``The HTK book'', for HTK version
3.2.1, Cambridege university engineering department

%*******************************  HMM ***************************

% Classical
\bibitem{RabinaHMM} L. R. Rabina, ``A tutorial on HMM and selected
applications in speech recognition'', Proceedings of IEEE, pp.
257-286, Vol. 77, No. 2, Feb. 1989
% Trended HMM
\bibitem{Deng92TrendedHMM} L. Deng, ``A generalized hidden Markov
model with state-conditioned trend functions of time for the speech
signal'', Signal Processing,  Vol. 27, No. 1, pp. 65-78, Apr. 1992
% Segmental HMM
\bibitem{Ostendorf96SegHMM} M. Ostendorf, V. V. Digalakis, O. A. Kimball,
``From HMM's to segment models: a unified view of stochastic
modeling for speech recognition'', IEEE Trans. on Speech and Audio
Processing, pp. 360-378, Vol. 4, No. 5, Sep., 1996
% Linear predictive HMM
\bibitem{Kenny91PredicHMM} P. Kenny, M. Lennig, P. Mermelstein, ``A linear predictive
HMM for vector-valued observations with applications to speech
recognition'', IEEE Trans. on Acoustics, Speech, and Signal
Processing, pp. 220-225, Vol. 38, No. 2, Feb., 1990

% EM

\bibitem{Dempster77EM} A. P. Dempster, N. M. Laird and D. B. Rubin,
``Maximum likelihood from incomplete data via the EM algorithm'',
Journal of  Royal Statistical Society, Vol. 39, pp. 1–38, 1977

% VAR

\bibitem{VAR_Lutkepohl} H. L\"{u}tkepohl, ``Introduction to multiple
time series analysis'', 2nd Ed., Springer-Verlag, 1993

\bibitem{Kenny90VAR} P. Kenny, M. Lennig and P. Mermelstein, ``A
linear predictive HMM for vector-valued observations with
applications to speech recognition'', IEEE Trans. on Acoustics,
Speech and Signal Processing, Vol. 38, No. 2, Feb. 1990

% ************************ Enhancement ****************************

% Subtraction
% Review of subtraction and Winer filter
\bibitem{JSLim79} J.S. Lim and A.V. Oppenheim, ``Enhancement and
bandwidth compression of noisy speech'',  Proceeding of the IEEE,
vol.67, no.12, pp.1586-1604, December 1979
% Subtraction
\bibitem{Berouti79} M. Berouti, R. Schwartz, and J. Makhoul,
``Enhancement of speech corrupted by acoustic noise'', in Proc. IEEE
ICASSP, pp. 208-211, Apr. 1979
% Noise masking
\bibitem{NVirag99Masking} N. Virag, ``Single channel speech enhancement based on
masking properties of the human auditory system'', IEEE Trans.
Speech and Audio Proc., vol. 7, no.2, Mar.1999
% Applications in speech recognition


% MMSE STSA
\bibitem{RJMcaulay} R. J. Mcaulay and M. L. Malpass, ``Speech enhancement
 using a soft-decision noise suppression filter'', IEEE Transactions
 on Acoustics, Speech, and Signal Processing, vol. ASSP-28, no. 2, Apr. 1980
\bibitem{YEphraim84} Y. Ephraim and D. Malah, ``Speech enhancement
 using a minimum mean square error short time spectral amplitude
 estimator'', IEEE Trans. Acoust., Speech, Signal Processing,
 vol. ASSP-32, pp. 1109-1121, Dec. 1984.
% Log domain
\bibitem{YEphraim85} Y. Ephraim and D. Malah, ``Speech enhancement
using a minimum mean square error Log-spectral amplitude
estimator'', IEEE Trans. Acoust., Speech, Signal Processing,vol.
ASSP-33, pp. 443-445, Apr. 1985.
% Analysis of MMSE STSA
\bibitem{OlivierCappe94} Olivier Capp\'{e}, ``Elimination of the
musical noise phenomenon with the Ephraim and Malah noise
suppressor'', IEEE Trans. Speech and Audio Proc., vol. 3, pp.
251-266, July 1995.
\bibitem{IYSoon_low_distortion_SE} I. Y. Soon and S. N. Koh, ``Low
distortion speech enhancement'', IEE Proc. on Vis. Image Signal
Process., vol. 147, no. 3, Jun. 2000
\bibitem{Hasan2004_a_priori_SNR} M. K. Hasan et al., ``A modified
\emph{a priori} SNR for speech enhancement using spectral
subtractoin rules'', IEEE Signal Processing Letters, vol. 11, no. 4,
Apr. 2004
\bibitem{ICohen} Israel Cohen, ``Speech Enhancement Using a
Noncausal \emph{A Priori} SNR Estimator'', IEEE Signal Processing
Letters, vol.11, no. 9, Sep. 2004
\bibitem{YiHu2004} Yi Hu and Philipos C. Loizou, ``Speech
enhancement based on wavelet thresholding the multitaper spectrum'',
IEEE Trans. on Speech Audio Processing, vol. 12, pp. 59-67, Jan.
2004.

% Subspace
\bibitem{Dendrinos} M. Dendrinos, S. Bakamidis, and G.
Carayannis, ``Speech enhancement from noise: A regenerative
approach'', Speech Commun., vol. 10, no. 2, pp. 45-57, Feb. 1991.
\bibitem{Jensen} S. H. Jensen, P. C. Hansen, S. D. Hansen,
and J. A. S{\o}ensen, ``Reduction of broad-band noise in speech by
truncated QSVD'',IEEE Trans. Speech Audio Processing, vol. 3, pp.
439-448, Nov. 1995.
\bibitem{YEphraim95} Y. Ephraim and H. L. Van Trees, ``A signal
subspace approach for speech enhancement'', IEEE Trans. Speech and
Audio Proc., vol. 3, pp. 251-266, July 1995.
\bibitem{Huang&Zhao} J. Huang and Y. Zhao, ``An energy-constraind
signal subspace method for speech enhancement and recognition in
colored noise'', in Proc. IEEE ICASSP, vol. 1, (Seattle), pp.
377-380, May 1998.
\bibitem{Rezayee} A. Rezayee and S. Gazor, ``An adaptive KLT
approach for speech enhancement'', IEEE Trans. Speech Audio
Processing, vol. 9, pp. 87-95, Feb. 2001.
\bibitem{Mittal} U. Mittal and N. Phamdo, ``Signal/noise
KLT based approach for enhancing speech degraded by colored noise'',
IEEE Trans. Speech Audio Processing, vol. 8, pp. 159-167, Mar. 2000.

% Noise effect

\bibitem{Dautrich83NoiseEffect} B. Dautrich, L. Rabiner, T. Martin, ``On the effects of
varying filter bank parameters on isolated word recognition'', IEEE
Trans. on Acoustics, Speech, Signal Processing, pp. 793-806,
ASSP-31, Aug. 1983

% signal modeling, feature extraction

\bibitem{Picone_sig_modeling} J. W. Picone, ``Signal modeling
techniques in speech recognition'', Proceedings of the IEEE, Vol.
81, No. 9, Sep. 1993

\bibitem{Ephraim99Cep} Y. Epraim and M. Rahim, ``On second order
statistics and linear estimation of cepstral coefficients'', IEEE
Trans. on speech and audio processing, pp. 162-176, Vol 7, No. 2,
1999

% math

\bibitem{Papoulis} A. Papoulis and S. U. Pillai, ``Probability,
random variables and stochastic processes'', 4th edition, McGraw
Hill, 2002

\bibitem{mathworld} MathWorld website, available at:
``http://mathworld.wolfram.com/''

% Books
%DSP
\bibitem{MitraDSP} S. K. Mitra, ``Digital signal processing: a
computer-based approach'', 2nd Edition, McGraw Hill, 2002
\bibitem{QuatieriDTSSP} T. F. Quatieri, ``Discrete-Time Speech Signal Processing:
Principles and Practice'', Prentice-Hall, 2001
\bibitem{Oppenheim99DTSP} A. V. Oppenheim and R. W. Schafer, with J. R. Buck.
``Discrete-Time Signal Processing'', 2nd Edition, Prentice-Hall,
Upper Saddle River, NJ, 1999
\bibitem{Oppenheim75DSP} A. V. Oppenheim and R. W. Schafer,
``Digital signal processing'', Englewood, NJ: Prentice-Hall, 1975
% Speech recognition
\bibitem{RabinaSR} L. Rabiner and B. H. Juang, ``Fundamentals of
Speech Recognition'', Prentice-Hall, 1993
% Spoken language processing
\bibitem{Huang00SpokenLangProc} X. D. Huang, A. Acero, H. W. Hon,
``Spoken language processing: A guide to theory, algorithm, and
system development'', Prentice-Hall 2001
% Statistical signal processing
\bibitem{KayEstimation} S. M. Kay, ``Fundamentals of statistical
signal processing: Estimation theory'', Prentice-Hall, 1993
% Hearing
\bibitem{Bekesy60Hearing} G. von B\'{e}k\'{e}sy, ``Experiments in Hearing'',
McGraw-Hill, New York, 1960
% Pattern classification
\bibitem{Duda01Pattern} R. O. Duda, P. E. Hart and D. G. Stork,
``Pattern classification'', 2nd edition, John Wiley \& Sons Inc.,
2001

% Normalization

\bibitem{MolauConf} S. Molau, et. al., ``Feature space normalization
in adverse acoustic conditions'', Proceedings of ICASSP 2003, Hong
Kong, Apr. 6-10, 2003

% ***************************** CMU ****************************

\bibitem{FuHua_Liu_CMN} F. Liu, et. al., ``Efficient cepstral
normalization for robust speech recognition'', Proceedings of ARPA
Human Language Technology Workshop, Mar. 1993
\bibitem{Acero_Aug_CMN} A. Acero, X. Huang, ``Augmented cepstral
normalization for robust speech recognition'', Proceedings of the
IEEE Workshop on Automatic Speech Recognition. Snowbird, UT. Dec
1995
\bibitem{Moreno_SC} P. J. Moreno, B. Raj, R. M. Stern, ``Data-driven
environmental compensation for speech recognition: A unified
appraoch'', Speech communication, pp. 267-285, Vol. 24, No. 4, Jul.
1998

% *************************Microsoft ***************************

%% SPLICE
%% Basic SPLICE
%\bibitem{Deng00SPLICE} L. Deng, A. Acero, M. Plumpe and X. D. Huang,
%``Large-vocabulary speech recognition under adverse acoustic
%environment'', in Proceeding of ICSLP, pp. 806-809, Vol. III, Oct.
%2000
%\bibitem{Deng01SPLICE} L. Deng, A. Acero, L. Jiang, J. Droppo and X. D.
%Huang, ``High-performance robust speech recognition using stereo
%training data'', in Proceeding of ICASSP, pp. 301-304, Vol I, Salt
%Lake City, Apr. 2001
%% Evaluation on AURORA-2
%\bibitem{Droppo01SPICE_AURORA2} J. Droppo, L. Deng and A. Acero,
%``Evaluation of the SPLICE algorithm on the Aurora2 database'', in
%Proceeding of European Conference on Speech Communication
%Technology, pp. 217-220, Aalborg, Denmark, Sep. 2001
%% Uncertainty decoding
%\bibitem{Droppo02SPLICE_Uncertainty} J. Droppo, L. Deng and A.
%Acero, ``Uncertainty decoding with SPLICE for noise robust speech
%recognition'', in Proceeding of ICASSP, pp. 57-60, Vol. I, Orlando,
%May 2002

\bibitem{Deng02ICASSP} L. Deng, J. Droppo and A. Acero, ``A Bayesian
approach to speech feature enhancement using the dynamic cepstral
prior'', Proceedings of ICASSP, pp. 829-832, Vol. 1, May 2002

\bibitem{Deng05Compare} L. Deng, J. Wu, J. Droppo and A. Acero,
``Analysis and comparison of two speech feature
extraction/compensation algorithms'', IEEE Signal Processing
Letters, pp. 477-480, Vol. 12, No. 6, Jun. 2005

\bibitem{Deng03Noise} L. Deng, J. Droppo, A. Acero, ``Recursive
estimation of nonstationary noise using iterative stochastic
approximation for robust speech recognition'', IEEE Trans. on Speech
and Audio Processing, pp. 568-580, Vol. 11, No. 6, Nov. 2003

\bibitem{Deng04Cep} L. Deng, J. Droppo and A. Acero, ``Estimating
cepstrum of speech under the presence of noise using a joint prior
of static and dynamic features'', IEEE Trans. on Speech and Audio
processing, pp. 218-223, Vol. 12, No. 3, May 2004

\bibitem{Deng04LogMel} L. Deng, J. Droppo and A. Acero,
``Enhancement of Log Mel power spectra of speech using a
phase-sensitive model of the acoustic environment and sequential
estimation of the corrupting noise'', IEEE Trans. on Speech and
Audio processing, pp. 133-143, Vol. 12, No. 2, Mar. 2004

\bibitem{Deng05Var} L. Deng, J. Droppo and A. Acero, ``Dynamic
compensation of HMM variances using the feature enhancement
uncertainty computed from a parametri model of speech distortion'',
IEEE Trans. on Speech and Audio processing, pp. 412421, Vol. 13, No.
3, May 2005

% Model adaptation

% PMC
\bibitem{Gales93PMC} M. J. F. Gales and S. J. Young, ``Cepstral
parameter compensation for HMM recognition'', Speech communication,
pp. 231-239, Vol. 12, 1993
% MLLR
\bibitem{Leggetter95MLLR} C. J. Leggetter and P. C. Woodland,
``Maximum likelihood linear regression for speaker adaptation of
continuous density hidden Markov models'', Computer Speech and
Language, pp. 171-185, No. 9, 1995
% MAP
\bibitem{Lee94MAP} J. L. Gauvain and C. H. Lee, ``Maximum
\emph{a~posterirori} estimation for multivariate Gaussian mixture
observations of Markov chains'', IEEE Trans. on Speech and Audio
Processing, pp. 291-298, Vol. 2, Apr. 1994
\bibitem{Huo95MAP} Q. Huo, C. Chan and C. H. Lee, ``Bayesian
adaptive learning of the parameters of hidden Markov model for
speech recgonition'', IEEE Trans. on Speech and Audio Processing,
pp. 334-345, Vol. 3, Sep. 1995
% Review
\bibitem{Lee98Review} C. H. Lee, ``On stochastic feature and model
compensation approaches to robust speech recognition'', Speech
Communication, pp. 29, 47, Vol. 25, 1998
% BPC
\bibitem{Huo00BPC} Q. Huo and C. Lee, ``A Bayesian predictive
approach to robust speech recognition'', IEEE Trans. on Speech and
Audio Processing, pp. 200-204, Vol. 8, No. 8, Nov. 2000

% Missing Feature
% Feature compensation
\bibitem{Raj05} B. Raj, R.M. Stern, ``Missing-feature approaches in
speech reconitoin'', \textit{Signal Processing Magazine}, vol. 22,
issue 5, pp. 101-116, Sep. 2005
\bibitem{Raj04} B. Raj, M.L. Seltzer, R.M. Stern, ``
Reconstruction of missing features for robust speech recognition'',
\textit{Speech Communication, vol. 43, no. 4, pp. 275-296, Sep.
2004}
% Classifier compensation
\bibitem{Cooke2001} M. Cooke, P. Green, L. Josifovski, Vizinho, A.,
``Robust automatic speech recognition with missing and uncertain
acoustic data'', \textit{Speech Communication}, vol. 34, pp.
267-285, 2001
\bibitem{Hugo03} Hugo Van hamme, ``Robust speech recognition using
missing feature theory in the cepstral or LDA domain'', Proceedings
of EuroSpeech, Geneva, Switzerland, pp. 3089-3092, Sep. 2003
\bibitem{Hugo04} H. Van hamme, ``Robust speech recognition using
cepstral domain missing data techniques and noisy mask'',
\textit{ICASSP 2004}

% Mask generation
% Bayesian classifier approach
\bibitem{Seltzer04Mask} M. L. Seltzer, B. Raj and R. M. Stern, ``A
Bayesian framework for spectrographic mask estimation for missing
feature speech recognition'', Speech Communication, pp. 379-393,
Vol. 43, No. 4, 2004
% Soft decision
\bibitem{Barker00Mask} J. Barker, L. Josifovski, M. Cooke and P.
Green, ``Soft decisions in missing data techniques for robust
automatic speech recognition'', in Proceedings of ICSLP 2000, pp.
373-376, Beijing, China, Sep. 2000
% Perceptual
\bibitem{Barker01MFT} J. Barker, M. Cooke and P. Green, ``Robust ASR
based on clean speech models: An evaluation of missing data
techniques for connected digit recognition in noise'', in
Proceedings of Eurospeech 2001, pp. 213-216, Aalborg, Denmark, 2001
\bibitem{Palomaki04Binaural} K. J. Palomaki, G. J. Brown and D. L.
Wang, ``A binaural processor for missing data speech recognition in
the presence of noise and small-room reverberation'', Speech
Communication, pp. 361-378, Vol. 43, No. 4, Sep. 2004

% Multiband

% PHD and Master Thesis

\bibitem{AceroPHD} A. Acero, ``Acoustical and environmental
robustness in automatic speech recognition'', PhD thesis, Dept. of
ECE, Carnegie Mellon University, 1990

\bibitem{OhshimaPHD} Y. Ohshima, ``Environmental robustness
in speech recognition using physiologically-motivated signal
processing'', PhD thesis, Dept. of ECE, Carnegie Mellon University,
1993

\bibitem{GalesPHD} M. J. F. Gales, ``Model-based techniques for
noise robust speech recognition'', PhD thesis, Gonville and Caius
College, University of Cambridge, 1995

\bibitem{MorenoPHD} P. J. Moreno, ``Speech recognition in noisy
environments'', PhD thesis, Dept. of ECE, Carnegie Mellon
University, 1996

\bibitem{RajPHD} B. Raj, ``Reconstruction of incomplete spectrograms
for robust speech recognition'', PhD thesis, Dept. of ECE, Carnegie
Mellon University, 2000

\bibitem{MolauPHD} S. Molau, ``Normalization in the acoustical
feature space for improved speech recognition'', PhD thesis, Aachen
University, 2003

\bibitem{CPChenPHD} C. P. Chen, ``Noise robustness in automatic
speech recognition'', PhD thesis, Electrical Engineering, University
of Washington, 2004

\bibitem{XiangLiPHD} X. Li, ``Combination and generation of Parallel
feature streams for improved speech recognition'', PhD thesis, Dept.
of ECE, Carnegie Mellon University, 2005

\bibitem{Furui_CMN} S. Furui, ``Cepstral analysis technique for automatic
speaker verification'', \textit{IEEE Trans. Acoust., Speech, Signal
Process}, vol. 29, no. 2, pp. 254-272, 1981

\bibitem{viikki_CVN} O. Viikki, D. Bye, and K. Laurila, ``A recursive feature vector
normalization approach for robust speech recognition in noise'',
\emph{In Proc. IEEE Int. Conf. Acoustics, Speech, Signal
Processing}, 1998, vol. 11, pp. 733-736

\bibitem{HEQ} A. de la Torre, A. M. Peinado, J. C. Segura, J. L. Perez-Cordoba,
M. C. Benitez and A. J. Rubio, ``Histogram equalization of speech
representation for robust Speech Recognition'', \textit{IEEE Trans.
Speech Audio Process.}, vol. 13, no. 3, pp. 355-366, 2005

\bibitem{RASTA} H. Hermansky and N. Morgan, ``RASTA processing of speech'', \emph{IEEE
Trans. Speech, Audio Proceess.}, vol. 2, no. 4, pp. 578-589, 1994

\bibitem{moduSpecImpt} N. Kanedera, T. Arai, H. Hermansky, and M. Pavel
``On the relative importance of various components of the modulation
spectrum for automatic speech recognition'', \emph{Speech
Commnunication}, vol. 28, No. 1, pp. 43-55, 1999

\bibitem{Hung} J.-W. Hung and L.-S. Lee, ``Optimization
of temporal filters for constructing robust features in speech
recognition'', \textit{IEEE Trans. Audio, Speech, Language
Process.}, vol. 14, no 3, pp. 808-832, May 2006

\bibitem{MVA1} C.-P. Chen, J. Blimes and K. Kirchhoff, ``Low-resource
noise-robust feature post-processing on AURORA 2.0'', In \emph{Proc.
ICSLP} 2002, pp. 2445-2448

\bibitem{AdvDSPVaseghi} S. V. Vaseghi, ``Advanced digital signal
processing and noise reduction'', 2nd Edition, John Wiley \& Sons,
LTD, 2000

\bibitem{DSP} J. G. Proakis and D. G. Manolakis, ``Digital signal
processing-principles, algorithms, and applications'', 3rd Edition,
Prentice-Hall, 1996

\end{thebibliography}
